### 2024-03-05 src/paper.tex
Minor fix
A few more fixes

    \node[state, initial, label=above left:$\Automaton{\RE{r}}$] (u0) {$\Pos\Char{a} \Spc \Char{b} \Spc \Char{c}$};
    \node[state, right=of u0] (u1) {$\Char{a} \Pos \Char{b} \Spc \Char{c}$};
    \node[state, accepting, right=of u1] (u2) {$\Char{a} \Spc \Char{b} \Pos \Char{c}$};
    \node[state, accepting, right=of u2] (u3) {$\Char{a} \Spc \Char{b} \Spc \Char{c}\Pos$};
    \draw (u0) edge[->] node[auto]{\Char{a}} (u1);
    \draw (u1) edge[->] node[auto]{\Char{b}} (u2);
    \draw (u2) edge[->] node[auto]{\Char{c}} (u3);
  \end{tikzpicture}
\end{center}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, accepting, label=above left:$\Automaton{R}$] (u0) {$\Pos\Char{a} \Spc \Char{a}$};
    \node[state, accepting, right=of u0] (u1) {$\Char{a} \Pos \Char{a}$};
    \node[state, accepting, right=of u1] (u2) {$\Char{a} \Spc \Char{a}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);
  \end{tikzpicture}
\end{center}

@@

    \node[state, initial, below=of u0, label=above left:$\Automaton{\RE{r}}$] (p0) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \node[state, accepting, right=of p0] (p1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (p0) edge[->] node[auto]{$\Char{a}$} (p1);
    \draw (p1) edge[->, loop right] node[auto]{$\Char{a}$} (p1);
  \end{tikzpicture}
\end{center}

@@

    \node[state, accepting, right=of v2] (v3) {$\begin{aligned}
      \N{\RE{r}} &= \KleenePlus{\{\Pos\Char{a}, \dots, \Pos\Char{z}\}}\\
      \N{\RE{p}} &= \Char{a} \Spc \Char{b}\\
      \underline{\N{\RE{q}}} &= \Char{a} \Spc \Char{b} \Spc \Char{c} \Pos\\
      \N{\RE{t}} &= \Char{a} \Spc \Char{c} \Spc \Char{d}
    \end{aligned}$};
    \draw (v2) edge[->] node[auto]{$\Char{c}$} (v3);

    \node[state, accepting, below right=of v1] (v4) {$\begin{aligned}
      \underline{\N{\RE{r}}} &= \KleenePlus{\{\Pos\Char{a}, \dots, \Pos\Char{z}\}}\\
      \N{\RE{p}} &= \Char{a} \Spc \Char{b}\\
      \N{\RE{q}} &= \Char{a} \Spc \Char{b} \Spc \Char{c}\\
      \N{\RE{t}} &= \Char{a} \Spc \Char{c} \Pos \Char{d}
    \end{aligned}$};

>>>>

    \node[state, initial, label=above left:$\Automaton{\RE{r}}$] (u0) {$\Pos\Char{a} \Spc \Char{b} \Spc \Char{c}$};
    \node[state, right=of u0] (u1) {$\Char{a} \Pos \Char{b} \Spc \Char{c}$};
    \node[state, right=of u1] (u2) {$\Char{a} \Spc \Char{b} \Pos \Char{c}$};
    \node[state, accepting, right=of u2] (u3) {$\Char{a} \Spc \Char{b} \Spc \Char{c}\Pos$};
    \draw (u0) edge[->] node[auto]{\Char{a}} (u1);
    \draw (u1) edge[->] node[auto]{\Char{b}} (u2);
    \draw (u2) edge[->] node[auto]{\Char{c}} (u3);
  \end{tikzpicture}
\end{center}

@@

\begin{center}
  \begin{tikzpicture}
    \tikzset{
      node distance=1cm,
      every state/.style={rectangle, rounded corners, inner sep=0.5em},
      initial text=$ $,
    }
    \node[state, initial, label=above left:$\Automaton{R}$] (u0) {$\Pos\Char{a} \Spc \Char{a}$};
    \node[state, right=of u0] (u1) {$\Char{a} \Pos \Char{a}$};
    \node[state, accepting, right=of u1] (u2) {$\Char{a} \Spc \Char{a}\Pos$};
    \draw (u0) edge[->] node[auto]{$\Char{a}$} (u1);
    \draw (u1) edge[->] node[auto]{$\Char{a}$} (u2);
  \end{tikzpicture}
\end{center}

@@

    \node[state, initial, below=of u0, label=above left:$\Automaton{\RE{r}}$] (p0) {$\KleenePlus{(\Pos\Char{a})}$};
    \node[state, accepting, right=of p0] (p1) {$\KleenePlus{(\Pos\Char{a})}\Pos$};
    \draw (p0) edge[->] node[auto]{$\Char{a}$} (p1);
    \draw (p1) edge[->, loop right] node[auto]{$\Char{a}$} (p1);
  \end{tikzpicture}
\end{center}

@@

    \node[state, accepting, right=of v2] (v3) {$\begin{aligned}
      \N{\RE{r}} &= \KleenePlus{\{\Pos\Char{a}, \dots, \Pos\Char{z}\}}\Pos\\
      \N{\RE{p}} &= \Char{a} \Spc \Char{b}\\
      \underline{\N{\RE{q}}} &= \Char{a} \Spc \Char{b} \Spc \Char{c} \Pos\\
      \N{\RE{t}} &= \Char{a} \Spc \Char{c} \Spc \Char{d}
    \end{aligned}$};
    \draw (v2) edge[->] node[auto]{$\Char{c}$} (v3);

    \node[state, accepting, below right=of v1] (v4) {$\begin{aligned}
      \underline{\N{\RE{r}}} &= \KleenePlus{\{\Pos\Char{a}, \dots, \Pos\Char{z}\}}\Pos\\
      \N{\RE{p}} &= \Char{a} \Spc \Char{b}\\
      \N{\RE{q}} &= \Char{a} \Spc \Char{b} \Spc \Char{c}\\
      \N{\RE{t}} &= \Char{a} \Spc \Char{c} \Pos \Char{d}
    \end{aligned}$};
